---
title: Chameleon Breeder Scorecard - iPardalis
header_title: iPardalis - Chameleon Breeder Scorecard
date: 2024-04-16
description: This is where we keep track of our performance and various statistics about our chameleon breeding program.
banner: img/banners/chameleon_breeder_stats
---

```{r}
#| echo: FALSE
require(plotly)
require(dplyr)
require(gt)
require(stringr)
require(fs)
require(glue)
require(readr)
require(yaml)
require(tidyr)
require(lubridate)
require(purrr)
require(here)
require(widgetframe)
require(DT)
require(plotly)
source(here("R/get_clutch_df.R"))

data <- get_raw_clutch_df(here("data/clutches/"), listed = FALSE)

distinct_clutches <- data %>% distinct(sire, dam, laid, hatchstart, hatchend, hatchnum, clutchsize, maleprice, femaleprice, sire_tree, sire_doh, dam_tree, dam_doh, lineage_collage) %>%
  arrange(laid)
write_csv(distinct_clutches, here("static/data.csv"))
```

# Chameleon Breeding Statistics
This is an article which dynamically pulls all our website data and shares it in figures and statistics about our chameleon breeding project. You can download it for yourself (below)! We are the first, and only, Panther Chameleon (Furcifer pardalis) breeder to track nearly a decade of our statistics and make them available to the public, free of charge.
<p>
<a class="btn btn-template-main" href="https://ipardalis.com/data.csv">Download Chameleon Breeding Data <i class="fas fa-download"></i></a>
</p>
> We'll be adding visualizations over the coming weeks, so feel free to reach out if you have ideas and we would be happy to hear from you :)

### Totals
**Dams**: `r distinct_clutches %>% distinct(dam) %>% nrow`
**Sires**: `r distinct_clutches %>% distinct(sire) %>% nrow`

**Clutches**: `r distinct_clutches %>% nrow`
**Eggs Laid**: `r sum(distinct_clutches$clutchsize, na.rm=T)`
**Babies Hatched**: `r sum(distinct_clutches$hatchnum, na.rm=T)`

## Dam Chart

```{r}
#| echo: FALSE
dam_plot <- distinct_clutches %>%
  plot_ly(
    x = ~laid,
    y = ~clutchsize,
    text = ~glue::glue("{clutchsize}: {sire} x {dam} <br>laid: {laid}"),
    hoverinfo = "text",
    color = ~dam
  ) %>%
  layout(
    xaxis = list(title="Clutch Laid (date)"),
    yaxis = list(title="Clutch Size")
  )
htmlwidgets::saveWidget(widget = dam_plot,
                        file = here("static/plot/dam_plot.html"),
                        selfcontained = TRUE)
```

{{{< iframe file_loc="plot/dam_plot.html" fig_width="100%" fig_height="600px" >}}}

## Interactive Table
You can search, sort and filter this table to view our breeding statistics however you'd like and click the images to view them full size! This level of transparency is unheard of. If you see any data errors or issues, feel free to bring them to our attention. We would be happy to fix them.

```{r dt_distinct_clutches}
#| echo: FALSE
clutches_dt <- distinct_clutches %>% 
  select(lineage_collage, sire, dam, laid, hatchstart, hatchend, clutchsize, hatchnum, sire_doh, sire_tree, dam_doh, dam_tree) %>%
  mutate(
    lineage_collage = glue("<a href='https://ipardalis.com{lineage_collage}' target='_blank'><img src='https://ipardalis.com{lineage_collage}' height='100px'></img></a>"),
    sire_tree = glue("<a href='https://ipardalis.com{sire_tree}' target='_blank'><img src='https://ipardalis.com{sire_tree}' height='100px'></img></a>"),
    dam_tree = glue("<a href='https://ipardalis.com{dam_tree}' target='_blank'><img src='https://ipardalis.com{dam_tree}' height='100px'></img></a>")
  ) %>%
  datatable(rownames=FALSE, escape = FALSE, filter = "top")

htmlwidgets::saveWidget(widget = clutches_dt,
                        file = here("static/dt/clutches_dt.html"),
                        selfcontained = TRUE)

```

{{{< iframe file_loc="dt/clutches_dt.html" fig_width="100%" fig_height="800px" >}}}

